Converting LaTeX R Journal Articles into Rmarkdown using texor and rebib

### 2023-07-26 texor.Rmd
Supplementary

# Structure of the \CRANpkg{texor} package

**DC: List the main functions in an organised way, could be the pre-processing functions, the post-processing functions, utility functions. This can be also be summarized in a table, but there needs to be text explanations of the main functionality.**

@@

@@

 github repos for the packages, texor, rebib, rjtools

>>>>

## Conversion

The only function that a user necessarily needs is `latex_to_web()`. This creates the R Journal style R Markdown file from a given R Journal style LaTeX file. 
This is achieved in several conversion steps, `convert_to_markdown()`, `generate_rmd()` and `produce_html()`.

## Handling figures

## Logging the conversion

@@

Run through the different examples in supplementary here

**From general LaTeX to generic R Markdown**

@@

Several supplementary example documents are provided which illustrate how different elements of LaTeX-authored papers are handled. These are:

-

The GitHub repos supporting this work are:

- \CRANpkg{texor}: https://abhi-1u.github.io/texor
- \CRANpkg{rebib}: https://abhi-1u.github.io/rebib/
- This paper: https://github.com/Abhi-1U/texor-rjarticle
- More details on \CRANpkg{rjtools} are at https://rjournal.github.io/rjtools/

### 2023-07-26 texor.tex
Supplementary

\hypertarget{structure-of-the-package}{%
\section{\texorpdfstring{Structure of the \CRANpkg{texor} package}{Structure of the  package}}\label{structure-of-the-package}}

\textbf{DC: List the main functions in an organised way, could be the pre-processing functions, the post-processing functions, utility functions. This can be also be summarized in a table, but there needs to be text explanations of the main functionality.}

@@

@@

github repos for the packages, texor, rebib, rjtools

>>>>

\hypertarget{conversion}{%
\subsection{Conversion}\label{conversion}}

The only function that a user necessarily needs is \texttt{latex\_to\_web()}. This creates the R Journal style R Markdown file from a given R Journal style LaTeX file.
This is achieved in several conversion steps, \texttt{convert\_to\_markdown()}, \texttt{generate\_rmd()} and \texttt{produce\_html()}.

\hypertarget{handling-figures}{%
\subsection{Handling figures}\label{handling-figures}}

\hypertarget{logging-the-conversion}{%
\subsection{Logging the conversion}\label{logging-the-conversion}}

@@

Run through the different examples in supplementary here

\textbf{From general LaTeX to generic R Markdown}

@@

Several supplementary example documents are provided which illustrate how different elements of LaTeX-authored papers are handled. These are:

\begin{itemize}
\tightlist
\item
\end{itemize}

The GitHub repos supporting this work are:

\begin{itemize}
\tightlist
\item
  \CRANpkg{texor}: \url{https://abhi-1u.github.io/texor}
\item
  \CRANpkg{rebib}: \url{https://abhi-1u.github.io/rebib/}
\item
  This paper: \url{https://github.com/Abhi-1U/texor-rjarticle}
\item
  More details on \CRANpkg{rjtools} are at \url{https://rjournal.github.io/rjtools/}
\end{itemize}
